Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Fixes

\subsection{Testing DAG Using CI Tests}
Our structure learning algorithm uses the idea of testing DAGs using CI tests.
In this section, we give an example of how this model testing works in
practice. We take the example of the MEC learned by the PC algorithm in
Figure~\ref{fig:intro}(b) using $ N=800 $. We first orient all the undirected
edges in the model based on our domain knowledge to obtain a DAG. In this case
we only have one undirected edge between \emph{Marital Status} and
\emph{Relationship} that we orient as $ \textrm{Marital Status} \rightarrow
\textrm{Relationship} $. We can now test the implied CIs of this DAG using
data. Figure~\ref{fig:ci_table} shows the result of this testing on some of the
implied CIs. If we use a p-value threshold of $ 0.05 $, the first $ 3 $ implied
CIs hold in the data whereas the remaining tests fail. One of the ways to fix
these failing tests is to add an edge between the variables $ X $ and $ Y $.
While this method tells up which variable pairs need to have an edge between
them, it does not tell anything about the orientation of the edge, and we would
need to orient it based on our domain knowledge.

>>>>

\subsection{Testing DAG Using CI Tests}
Our structure learning algorithm uses the idea of testing DAGs using CI tests.
In this section, we give an example of how this model testing works in
practice. We take the example of the MEC learned by the PC algorithm in
Figure~\ref{fig:intro}(b) using $ N=800 $. We first orient all the undirected
edges in the model based on our domain knowledge to obtain a DAG. In this case
we only have one undirected edge between \emph{Marital Status} and
\emph{Relationship} that we orient as \emph{Marital Status} $ \rightarrow $
\emph{Relationship} . We can then test the implied CIs of the DAG using our
dataset. Figure~\ref{fig:ci_table} shows the result of this testing on some of
the implied CIs. If we use a p-value threshold of $ 0.05 $, the first $ 2 $
implied CIs hold in the data whereas the remaining tests fail. One of the ways
to fix these failing tests is to add an edge between the variable pair $ X $
and $ Y $. While this method helps us in finding variable pairs where we need
to add an edge, it does not give us any information about the orientation of
this edge. We would have to rely on domain knowledge to determine this
orientation.
